Bayesian inference of prehistoric demography from multiple proxies: a case study from the Swiss plateau

### 2022-05-19 manuscript/paper.Rmd
Suggest new title and alternatives

title: "Bayesian Hierarchical Model for estimating holocene prehistoric population development on the Swiss Plateau"

@@

>>>>

title: "Bayesian inference of prehistoric demography from multiple proxies: a case study from the Swiss plateau"

@@

<!--
[JR] suggested alternative titles:
* A Bayesian hierarchical model of prehistoric population dynamics on the Swiss Plateau
* Multi-proxy estimation of prehistoric population dynamics on the Swiss Plateau using Bayesian hierarchical modelling
* Combining multiple proxies to estimate prehistoric population dynamics on the Swiss Plateau using Bayesian hierarchical modelling
* A high-resolution estimate of prehistoric population dynamics on the Swiss Plateau using multi-proxy Bayesian hierarchical modelling
* Prepend "Beyond summed radiocarbon:" to any of the above
* Bayesian inference of prehistoric demography from multiple proxies: a case study from the Swiss plateau
-->
